---
output:
  pdf_document: default
  html_document: default
---
```{r details for the year, echo=FALSE}

conference_year <- "2021"
organizing_com_chair <- c("Org Com Chair", "Dr.", "University of Awesome")
organizing_com_mem_1 <- "Another member"

```

# Introduction {#intro}

This is a basic example of different aspects of bookdown to demonstrate how to use. 

In `r conference_year` the organizing committee will be chaired by `r organizing_com_chair[2]` `r organizing_com_chair[1]` from the `r organizing_com_chair[3]`. 

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
